---
title: "Elicitation Analysis"
author: "Team Mindset"
date: "July 15, 2014"
output: html_document
---

# Elicitation Analysis

```{r, echo=F, message=F}
library(knitr)
library(ggplot2)
library(plyr)
library(bear)
text.size = 12
mindset.hist = function(r) {
  ggplot(r, aes(x=entityScore)) + 
  geom_histogram(aes(y=..density.., fill=factor(mindset)),
                 # Histogram with density instead of count on y-axis
                 binwidth=1, colour="black") +
  geom_density(alpha=.2, fill="#080808") +
  theme_bw(text.size)
}
```

## Theories

```{r echo=F}
theory.filter = function(r, all.subjects) {
  return(
    all.subjects[
      sapply(as.character(all.subjects),
             function(subj){
               r$sanity0[r$workerID==subj][1] <= 0.1 &
                 r$sanity1[r$workerID==subj][1] >= 0.9
               })])}
load = function(filename, split="median") {
  r = read.table(filename, header=T, sep=",")
  r$entityScore = r$entity1 + r$entity2 + (7 - r$increm1) + (7 - r$increm2)
  
  # group people into growth and fixed
  med.split = median(r$entityScore)
  up.quart = median(r$entityScore[r$entityScore > med.split])
  low.quart = median(r$entityScore[r$entityScore < med.split])
  
  if (split == "median") {
    r$mindset <- ifelse(r$entityScore > med.split, "fixed", "growth")
  } else if (split == "quartile") {
    r$mindset <- ifelse(r$entityScore >= up.quart, "fixed", NA)
    r$mindset[r$entityScore <= low.quart] = "growth"
    r = r[!is.na(r$mindset),]
  }
  
  #factors and labels
  r$e = factor(r$effort, levels=c("low", "medium", "high"),
               labels=c("0", "0.5", "1"))
  r$a = factor(r$ability, levels=c("low", "high"),
               labels=c("0.5", "1"))
  r$d = factor(r$difficulty, levels=c("easy", "difficult"),
               labels=c("0.2", "2"))
  r$e = as.numeric(as.character(r$e))
  r$a = as.numeric(as.character(r$a))
  r$d = as.numeric(as.character(r$d))
  
  #factors and labels
  r$effort = factor(r$effort, levels=c("low", "medium", "high"),
                    labels=c("Low effort", "Medium effort", "High effort"))
  r$ability = factor(r$ability, levels=c("low", "high"),
                     labels=c("Low ability", "High ability"))
  r$difficulty = factor(r$difficulty, levels=c("easy", "difficult"),
                        labels=c("Easy", "Difficult"))
  
  return(r)
}
plot.all = function(r, theory) {
  theory.all <- subset(r, theoryType==theory)
  print(ggplot(theory.all, aes(x=entityScore, y=response, color=effort)) +
      geom_smooth(method=lm) +
      facet_grid(difficulty ~ ability) +
      theme_bw(text.size) +
      xlab("Fixedness") +
      ylab("Performance") #+ ggtitle(r.title)
      )
}
plot.discrete.effort = function(r, theory) {
  summary = summarySE(subset(r, theoryType==theory),
                           measurevar="response",
                           groupvars=c("ability", "effort",
                                       "difficulty", "mindset"))
  print(ggplot(summary,
       aes(x=effort, y=response, color=mindset)) +
  geom_errorbar(aes(ymin=response-ci, ymax=response+ci), width=0.2, color="grey") +
  geom_point(size=3) +
  facet_grid(difficulty ~ ability) +
  theme_bw(text.size) +
  xlab("") +
  ylab(theory))
}

plot.continuous.effort = function(r) {
  ggplot(r, aes(x=e, y=response, color=mindset)) +
    geom_point(alpha=1/3) +
    facet_grid(. ~ theoryType) +
    theme_bw(text.size) +
    stat_smooth(method="lm") +
    xlab("effort") +
    ylab("response")
}
plot.just.mindset = function(r, theory) {
  theory.all <- subset(r, theoryType==theory)
  justMindset <- summarySE(theory.all, measurevar="response",
                                       groupvars=c("mindset"))
  ggplot(justMindset, aes(x=mindset, y=response, fill=mindset)) +
    geom_bar(stat="identity", color="black") +
    geom_errorbar(aes(ymin=response-ci, ymax=response+ci), width=0.2) +
    theme_bw(text.size) +
    ylab(theory) +
    xlab("Mindset")
}

```

### Pilot (R0)

```{r echo=F}
theories.r0 = load("../data/theories-r0.csv")
all.subjects = unique(theories.r0$workerID)
good.subjects = theory.filter(theories.r0, all.subjects)
# improvement <- summarySE(subset(r, theoryType=="improvement"),
#                          measurevar="response",
#                          groupvars=c("ability", "effort", "difficulty", "mindset"))
```

There were `r length(all.subjects)` Ss total, `r length(good.subjects)` of whom passed attention checks.

Here were Ss' entity scores (higher scores indicate more endorsement of entity theories):

```{r fig.width=7, fig.height=3, echo=F}
print(mindset.hist(theories.r0))
```

Median entity score (used for split) was `r median(theories.r0$entityScore)`.

People with different mindsets did not differ in their overall prediction of success:

```{r fig.width=4, fig.height=2, echo=F}
plot.just.mindset(theories.r0, "performance")
```

People with "growth" mindsets predicted more improvement overall than did people with "fixed" mindsets:

```{r fig.width=4, fig.height=2, echo=F}
plot.just.mindset(theories.r0, "improvement")
```

People with more "growth" mindsets (lower entity scores) may think people are less likely to succeed at difficult tasks without trying (lower left, red line).

Performance as a function of entity score:

```{r fig.width=7, fig.height=3, echo=F}
plot.all(theories.r0, "performance")
```

Performance as a function of effort:

```{r fig.width=7, fig.height=3, echo=F}
plot.discrete.effort(theories.r0, "performance")
```

Improvement as a function of effort:

```{r fig.width=6, fig.height=3, echo=F}
plot.discrete.effort(theories.r0, "improvement")
```

People with different mindsets seem to differ in how much they think effort matters to improvement, but not in how much effort matters to success:

Performance and improvement as a function of effort:

```{r fig.width=7, fig.height=3, echo=F}
plot.continuous.effort(theories.r0)
```

### "Replication" with goals

```{r echo=F}
theories.with.goals.r0 = load("../data/theories-with-goals-r0.csv")
all.subjects = unique(theories.with.goals.r0$workerID)
good.subjects = theory.filter(theories.with.goals.r0, all.subjects)
```

There were `r length(all.subjects)` Ss total, `r length(good.subjects)` of whom passed attention checks.

Here were Ss' entity scores (higher scores indicate more endorsement of entity theories):

```{r fig.width=7, fig.height=3, echo=F}
print(mindset.hist(theories.with.goals.r0))
```

Median entity score (used for split) was `r median(theories.r0$entityScore)`.

People with different mindsets did not differ in their overall prediction of success:

```{r fig.width=4, fig.height=2, echo=F}
plot.just.mindset(theories.with.goals.r0, "performance")
```

People with "growth" mindsets did not differ in their overall prediction of improvment (this is different from what we found in the pilot):

```{r fig.width=4, fig.height=2, echo=F}
plot.just.mindset(theories.with.goals.r0, "improvement")
```

{{{{{{{{}}}}}}}}

Performance as a function of entity score:

```{r fig.width=7, fig.height=3, echo=F}
plot.all(theories.with.goals.r0, "performance")
```

Performance as a function of effort:

```{r fig.width=7, fig.height=3, echo=F}
plot.discrete.effort(theories.with.goals.r0, "performance")
```

Improvement as a function of effort:

```{r fig.width=6, fig.height=3, echo=F}
plot.discrete.effort(theories.with.goals.r0, "improvement")
```

{{{{{{{{{{{{People with different mindsets seem to differ in how much they think effort matters to improvement, but not in how much effort matters to success:}}}}}}}}}

Performance and improvement as a function of effort:

```{r fig.width=7, fig.height=3, echo=F}
plot.continuous.effort(theories.with.goals.r0)
```



## hi

```{r fig.width=7, fig.height=4, echo=F}
theories.with.goals.r0 = load("../data/theories-with-goals-r0.csv")
all.subjects = unique(theories.with.goals.r0$workerID)
good.subjects = theory.filter(theories.with.goals.r0, all.subjects)
```

There were `r length(all.subjects)` Ss total, `r length(good.subjects)` of whom passed attention checks.

#### Responses to mindset questionnaire

Here were Ss' entity scores (higher scores indicate more endorsement of entity theories):

```{r fig.width=7, fig.height=3, echo=F}
print(mindset.hist(theories.with.goals.r0))
```

Median entity score (used for split) was `r median(theories.with.goals.r0$entityScore)`.

#### Performance

Performance as a function of entity score:

```{r fig.width=7, fig.height=3, echo=F}
plot.performance.all(theories.with.goals.r0)
```

Performance as a function of effort:

```{r fig.width=6, fig.height=3, echo=F}
plot.discrete.effort(theories.with.goals.r0, "performance")
```

People with different entity scores do not seem to differ in their theories of performance.

#### Improvement

Improvement as a function of effort:

```{r fig.width=7, fig.height=3, echo=F}
plot.discrete.effort(theories.with.goals.r0, "improvement")
```

#### Performance and Improvement

Performance and improvement as a function of effort:

```{r fig.width=7, fig.height=3, echo=F}
plot.continuous.effort(theories.with.goals.r0)
```

### Replication without goals (R1)

```{r fig.width=7, fig.height=4, echo=F}
theories.r1 = load("../data/theories-r1.csv")
all.subjects = unique(theories.r1$workerID)
good.subjects = theory.filter(theories.r1, all.subjects)
```

There were `r length(all.subjects)` Ss total, `r length(good.subjects)` of whom passed attention checks.

Here were Ss' entity scores (higher scores indicate more endorsement of entity theories):

```{r fig.width=7, fig.height=3, echo=F}
print(mindset.hist(theories.r1))
```

Median entity score (used for split) was `r median(theories.r1$entityScore)`.

## Goals

```{r fig.width=7, fig.height=4, echo=F}
goals.r0 = read.table("../data/goals-r0.csv", header=T, sep=",")
```